Geometric models reveal the hidden structure of conceptual knowledge

### 2023-01-20 paper/main.tex
added demographics survey responses, demographic survey notebook, and methods text reporting participant survey results

>>>>

We enrolled a total of 50 Dartmouth undergraduate students in our study.
Participants received course credit for enrolling. We asked each participant to
fill out a demographic survey that included questions about their age, gender,
native spoken language, ethnicity, race, hearing, color vision, sleep, coffee
consumption, level of alertness, and several aspects of their educational
background and prior coursework.

Participants' ages ranged from 18 to 22 years (mean: 19.52 years;
standard deviation: 1.09 years). A total of 15 participants reported
their gender as male and 35 participants reported their gender as
female. A total of 49 participants reported their native language as
``English'' and 1 reported having another native language. A total of
47 participants reported their ethnicity as ``Not Hispanic or Latino''
and three reported their ethnicity as ``Hispanic or Latino.''
Participants reported their races as White (32 participants), Asian
(14 participants), Black or African American (5 participants),
American Indian or Alaska Native (1 participant), and Native Hawaiian or
Other Pacific Islander (1 participant). (Note that some participants
selected multiple recial categories.)

A total of 49 participants reporting having normal hearing and 1
participant reported having some hearing impairment. A total of 49
participants reported having normal color vision and 1 participant
reported being color blind.  Participants reported having had, on the
night prior to testing, 2 -- 4 hours of sleep (1 participant), 4 -- 6
hours of sleep (9 participants), 6 -- 8 hours of sleep (35
participants), or $8+$ hours of sleep (5 participants). They reported
having consumed, on the same day and leading up to their testing
session, 0 cups of coffee (38 participants), 1 cup of coffee (10
participants), 3 cups of coffee (1 participant), or $4+$ cups of
coffee (1 participant).

No participants reported that their focus was currently impaired
(e.g., by drugs or alcohol).  Participants reported their current
level of alertness, and we converted their responses to numerical
scores as follows: ``very sluggish'' (-2), ``a little sluggish'' (-1),
``neutral'' (0), ``fairly alert'' (1), and ``very alert'' (2). Across
all participants, a range of alertness levels were reported (range: -2
-- 1; mean: -0.10; standard deviation: 0.84).

Particpants reported their undergraduate major(s) as Social Sciences
(28 participants), Natural sciences (16), Professional (e.g., pre-med
or pre-law; 8 participants), Mathematics and engineering (7
participants), Humanities (4 participants), or Undecided (3
participants).  Note that some participants selected multiple
categories for their undergraduate major.  We also asked participants
about the courses they had taken.  In total, 46 participants reported
having taken at least one Khan academy course in the past or being
familiar with the Khan academy, and 4 reported not having taken any
Khan academy courses.  Of the participants who reported having watched
at least one Khan academy course, 1 participant declined to report the
number of courses they had watched; 7 participants reported having
watched 1--2 courses; 11 reported having watched 3--5 courses; 8
reported having watched 5--10 courses; and 19 reported having watched
10 or more courses.  We also asked participants about the specific
courses they had watched, categorized under different subject areas.
In the ``Mathematics'' area participants reported having watched
videos on AP Calculus AB (21 participants), Precalculus (17
participants), Algebra 2 (14 participants), AP Calculus BC (12
participants), Trigonometry (11 participants), Algebra 1 (10
participants), Geometry (8 participants), Pre-algebra (7
participants), Multivariable Calculus (5 participants), Differential
Equations (5 participants, Statistics and Probability (4
participants), AP Statistics (2 participants), Linear Algebra (2
participants), Early Math (1 participant), Arithmetic (1 participant),
and other videos not listed in our survey (6 participants).  In the ``Science and engineering''
area participants reported having watched videos on Chemistry, AP
Chemistry, or Organic Chemstry (21
participants); Physics, AP Physics I, or AP Physics II (15 participants); Biology, AP
Biology; or High school Biology (15 participants); Health and Medicine
(1 participant); or other videos not listed in our survey (20 participants).  We also asked
participants if they had specifically seen the videos used in our
experiment.  When we asked about the \textit{Four Fundamental Forces}
video, 45 participants reported not having watched it before, 1
participant reported that they were not sure if they had watched it
before, and 4 participants declined to respond.  When we asked about
the \textit{Birth of Stars} video, 46 participants reported not having
watched it before and 4 participants declined to respond.  When we
asked participants about non-Khan academy online courses, they
reported having watched or taken courses on Mathematics (15
participants), Science and engineering (11 participants), Test
preparation (9 participants), Economics and finance (3 participants),
Arts and humanities (2 participants), Computing (2 participants), and
other categories not listed in our survey (18 participants).  Finally,
we asked participants about in-person courses they had taken in
different subject areas.  They reported taking courses in Mathematics
(39 participants), Science and engineering (38 participants), Arts and
humanities (35 participants), Test preparation (27 participants),
Economics and finance (26 participants), Computing (15 participants),
College and careers (7 participants), or other courses not listed in
our survey (6 participants).

% alertness + impairments

% education
